---
title: "Untitled"
output: html_document
---

# Problem
We are attempting to predict if a person is likely to have be a high risk when we lend them money.

We are analyzing a dataset with over 30,000 entries of previous customers and their risk level for Stark Enterprises. We are building a decision tree with that data and using it for our predictions. 

This data comprises dozens of variables about previous customers who applied for credit. We narrowed the variables down to a small handful we thought would be useful. We chose CNT_CHILDREN, AMT_INCOME_TOTAL, AMT_CREDIT, AMT_ANNUITY,    AMT_GOODS_PRICE, and DAYS_EMPLOYED as our variables. 

```{r}
library(rpart)
library(rpart.plot)
library(forecast)
library(tidyr)
library(caret)
library(ROSE)
```

```{r}
cred <- read.csv("credit_8.csv", header = TRUE)
names(cred)
```

```{r}
cred <- drop_na(cred)
```

```{r}
head(cred,10)
str(cred)
```

```{r}
# Choosing to only keep columns that seem like they're good predictors
cred <- cred[ , c(3, 8:12, 19)]
names(cred)
```

```{r}
cred$cat_TARGET <- ifelse(cred$TARGET <= mean(cred$TARGET, na.rm = TRUE), 0, 1)
```

```{r}
set.seed(1331)
```

```{r}
train_index <-sample(1:nrow(cred), 0.6*nrow(cred))
valid_index <-setdiff(1:nrow(cred), train_index)
```

```{r}
train_df <- cred[train_index, ]
valid_df <- cred[valid_index, ]
```

```{r}
nrow(train_df)
nrow(valid_df)
```

```{r}
#Balancing data
train_df$TARGET <- as.factor(train_df$TARGET)
train_df_balanced <- ROSE(TARGET ~  CNT_CHILDREN 
                          + AMT_INCOME_TOTAL + AMT_CREDIT 
                          + AMT_ANNUITY 
                          + AMT_GOODS_PRICE 
                          + DAYS_EMPLOYED,
                          data = train_df, seed = 1331)$data
```

```{r}
table(train_df_balanced$TARGET)
```

```{r}
#Classification tree
class_tr <- rpart(TARGET ~ CNT_CHILDREN 
                  + AMT_INCOME_TOTAL + AMT_CREDIT 
                  + AMT_ANNUITY 
                  + AMT_GOODS_PRICE 
                  + DAYS_EMPLOYED,
                  data = train_df_balanced, method = "class", maxdepth = 20)
prp(class_tr)
```
```{r}
rpart.plot(class_tr, type = 5)
rpart.rules(class_tr, extra = 4)
```
```{r}
library(janitor)
compare_df_cols(train_df,valid_df)
valid_df$TARGET <- as.factor(valid_df$TARGET)
```

```{r}
#Confusion matrices
class_tr_train_predict <- predict(class_tr, train_df_balanced,
                                  type = "class")
confusionMatrix(class_tr_train_predict, train_df_balanced$TARGET,
                positive = "1")
```

```{r}
class_tr_valid_predict <- predict(class_tr, valid_df,
                                  type = "class")

confusionMatrix(class_tr_valid_predict, valid_df$TARGET,
                positive = "1")
```

```{r}
#Probabilities
class_tr_valid_predict_prob <- predict(class_tr, valid_df,
                                       type = "prob")
head(class_tr_valid_predict_prob)
```

```{r}
# Implementing new records
new_record_class <- data.frame(CNT_CHILDREN = 0,
                               AMT_INCOME_TOTAL = 180000,
                               AMT_CREDIT = 383760, 
                               AMT_ANNUITY = 40428, 
                               AMT_GOODS_PRICE = 360000, 
                               DAYS_EMPLOYED = -1304)
class_tr1 <- predict(class_tr, newdata = new_record_class)
class_tr1


new_record_class2 <- data.frame(CNT_CHILDREN = 0,
                               AMT_INCOME_TOTAL = 292500,
                               AMT_CREDIT = 675000, 
                               AMT_ANNUITY = 24376.5, 
                               AMT_GOODS_PRICE = 675000, 
                               DAYS_EMPLOYED = -1548)
class_tr2 <- predict(class_tr, newdata = new_record_class2)
class_tr2

new_record_class3 <- data.frame(CNT_CHILDREN = 0,
                               AMT_INCOME_TOTAL = 157500,
                               AMT_CREDIT = 761067, 
                               AMT_ANNUITY = 33655.5, 
                               AMT_GOODS_PRICE = 657000, 
                               DAYS_EMPLOYED = -2124)
class_tr3 <- predict(class_tr, newdata = new_record_class3)
class_tr3

new_record_class4 <- data.frame(CNT_CHILDREN = 0,
                               AMT_INCOME_TOTAL = 90000,
                               AMT_CREDIT = 67500, 
                               AMT_ANNUITY = 7047, 
                               AMT_GOODS_PRICE = 67500, 
                               DAYS_EMPLOYED = 365243)
class_tr4 <- predict(class_tr, newdata = new_record_class4)
class_tr4

new_record_class5 <- data.frame(CNT_CHILDREN = 3,
                               AMT_INCOME_TOTAL = 135000,
                               AMT_CREDIT = 301464, 
                               AMT_ANNUITY = 20277, 
                               AMT_GOODS_PRICE = 238500, 
                               DAYS_EMPLOYED = -989)
class_tr5 <- predict(class_tr, newdata = new_record_class5)
class_tr5
```

# Final Model

As you can see, we have 5 predictions, one for each of our new records. We think our model is solid and accurate with it's predictions. It's also very informative and allows us to make good recommendations to Stark Enterprises. 